Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-04 paper/ms.tex
Add figure to explain range-dphi plot

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to
$\pm\Delta\phi/2$.}
\label{fig:range_deltaphi}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/fig_to_explain.pdf}
\caption{A cartoon explanation of Figure~\ref{fig:range_deltaphi}. An observer
is placed at the blue x in the plane of a backgrround galaxy (lime). For a
given $\Delta \phi$ (blue) centered on the observer, we record the range of
midplane values for this section of the Solar circle (orange). We plot the
value of the range against the value of $\Delta \phi$. We are also able to
convert the value of $\Delta \phi$ into a chord length (pink), which we plot
as a secondary, upper $x$-axis. We repeat the procedure for each initial
$\phi$ (gray lines), and also compute the mean and $\pm1\,\sigma$ values (dark
blue).}
\label{fig:fig_to_explain}
\end{figure*}

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to $\pm\Delta\phi/2$.
A cartoon explanation of this Figure is given in
Figure~\ref{fig:fig_to_explain}.}
\label{fig:range_deltaphi}
\end{figure*}
